Classless Java: Tuning Java Interfaces

### 2016-03-15 OOPSLA16/sections/Implementation.tex
Reviewed the new H text, improved a little the examples

\begin{figure*}[t]\label{fig:lombok}
\centering
\includegraphics[width=5in]{pdfs/lombok.png}
\caption{The flow chart of Lombok annotation processing. [Ref: http://notatube.blogspot.hk/2010/12/project-lombok-creating-custom.html]}
\end{figure*}

@@

\item \textbf{No reuse of the type system.}
As we mentioned above, badly designed rewritings can arise from the great power of Lombok. A simple piece of source code
\begin{lstlisting}
interface M { int m(); }
\end{lstlisting}
can be reinterpreted as
\begin{lstlisting}
interface M { void m(String s); }
\end{lstlisting}
in which case the type of method \Q@m@ is changed. Our \mixin annotation does not introduce this kind of rewritings,
and hence the type system is reused. Moreover, Lombok can also modify unbounded types, which is easy to understand,
for instance, the following code
\begin{lstlisting}
interface M { T m(); } // T is unbounded
\end{lstlisting}
is transformed into
\begin{lstlisting}
interface M { int m(); } // No error message
\end{lstlisting}
in which case the user will see the unbounded type in source code, but without error message from the compilation, since
Lombok has modified the return type of \Q@m@. However, our \mixin annotation can still keep such errors and warnings.

In our annotation, we only enhance code:
we satisfy the behaviour of abstract methods, we add methods and we refine return types.
We consider this to be quite easy to follow, since it is similar to what happens in normal inheritance.

>>>>

\begin{figure*}[t]\label{fig:lombok}
\centering
\includegraphics[width=5in]{pdfs/lombok.png}
\caption{The flow chart of Lombok annotation processing. [Ref: http://notatube.blogspot.hk/2010/12/project-lombok-creating-custom.html]
\marco{I'm not sure this helps: It is trying to show the "eclipse" path, that is the one we implemented,
but there is also the "javac" path, and here we call the graph "Lombok annotation processing".
May be this should be "obj" processing?
}}
\end{figure*}

@@

Our annotation reinterpret the syntax for the sole goal of enhance/complete code:
we satisfy the behaviour of abstract methods, we add methods and we refine return types.
We consider this to be quite easy to follow, since it is similar to what happens in normal inheritance.

\marco{The section No reuse of the type system
is controversial.
We do need to repeat the type checking, plus we aim to make untypable stuff well typed
(for example anyone using the of method would not be well typed before).}
%\item \textbf{No reuse of the type system.}
%As we mentioned above, badly designed rewritings can arise from the great power of Lombok. A simple piece of source code
%\begin{lstlisting}
%interface M { int m(); }
%\end{lstlisting}
%can be reinterpreted as
%\begin{lstlisting}
%interface M { void m(String s); }
%\end{lstlisting}
%in which case the type of method \Q@m@ is changed. Our \mixin annotation does not introduce this kind of rewritings,
%and hence the type system is reused. Moreover, Lombok can also modify unbounded types, which is easy to understand,
%for instance, the following code
%\begin{lstlisting}
%interface M { T m(); } // T is unbounded
%\end{lstlisting}
%is transformed into
%\begin{lstlisting}
%interface M { int m(); } // No error message
%\end{lstlisting}
%in which case the user will see the unbounded type in source code, but without error message from the compilation, since
%Lombok has modified the return type of \Q@m@. However, our \mixin annotation can still keep such errors and warnings.
